Benchmarks of the Non-Relativistic Hydrodynamics Algorithms in \thornado

### 2017-02-13 Documents/Euler/Benchmarks1D/draft.tex
Added description of time stepping

\usepackage{amsfonts}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{amsthm}
\usepackage{booktabs}
\usepackage{mathrsfs}
\usepackage{cite}
%\usepackage{times}
\usepackage{url}
%\usepackage{hyperref}
\usepackage{natbib}
%\hypersetup{
 % bookmarksnumbered = true,
  %bookmarksopen=false,
  %pdfborder=0 0 0,         % make all links invisible, so the pdf looks good when printed
  %pdffitwindow=true,      % window fit to page when opened
  %pdfnewwindow=true, % links in new window
  %colorlinks=true,           % false: boxed links; true: colored links
  %linkcolor=blue,            % color of internal links
  %citecolor=magenta,    % color of links to bibliography
  %filecolor=magenta,     % color of file links
  %urlcolor=cyan              % color of external links
%}
\usepackage{graphicx}
\graphicspath{ {figures/} }

\newcommand{\thornado}{\texttt{thornado}}

@@

@@

Several tests were used to assess the accuracy of the integration method \citep{LiskaWendroff2003}. 
\begin{table}[h!]
\begin{center}
\begin{tabular}{ |c|c c c|c c c|c c| }
 \hline
 Test & $\rho_L$ & $u_L$ & $p_L$ & $\rho_R$ & $u_R$ & $p_R$ & $x_0$ & T \\
 \hline
 1 & 1 & 0 & 1 & 0.125 & 0 & 0.1 & 0.5 & 0.2 \\
 2 & 1 & 0.75 & 1 & 0.125 & 0 & 0.1 & 0.3 & 0.2 \\
 3 & 1 & -2 & 0.4 & 1 & 2 & 0.4 & 0.5 & 0.15 \\
 4 & 1 & 1 & $10^{-6}$ & 1 & -1 & $10^{-6}$ & 0.5 & 1 \\
 5 & 1 & -19.59745 & 1000 & 1 & -19.59745 & 0.01 & 0.8 & 0.012 \\
 6 & 5.99924 & 19.5975 & 460.894 & 5.99242 & -6.19633 & 46.095 & 0.4 & 0.035 \\
 7 & 1.4 & 0 & 1 & 1 & 0 & 1 & 0.5 & 2 \\
 8 & 1.4 & 0.1 & 1 & 1 & 0.1 & 1 & 0.5 & 2 \\
 9 & 0.1261192 & 8.9047029 & 782.92899 & 6.591493 & 2.2654207 & 3.1544874 & 0.5 & 0.0039 \\
10 & 5.6698 & 9.0299 & 100 & 1.0 & 0.0 & 1.0 & 0 & 1 \\
11 & 5.6698 & −1.4701 & 100 & 1.0 & -10.5 & 1.0 & 0 & 1 \\
 \hline
\end{tabular}
  \caption{table of tests}
  \label{tab:testtable}
\end{center}
\end{table}
$x_0$ refers to the position of the barrier. The computational domain is 0.0 to 1.0 in tests 1--8, 0.1 to 0.6 in test 9 \citep{LiskaWendroff2003}, -5 to 15 in test 10, and -15 to 5 in test 11 \citep{Leveque2003}.

>>>>

\usepackage{amsfonts}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{amsthm}
\usepackage{booktabs}
%\usepackage{mathrsfs}
\usepackage{cite}
%\usepackage{times}
\usepackage{url}
%\usepackage{hyperref}
\usepackage{natbib}
\usepackage{color}
%\hypersetup{
 % bookmarksnumbered = true,
  %bookmarksopen=false,
  %pdfborder=0 0 0,         % make all links invisible, so the pdf looks good when printed
  %pdffitwindow=true,      % window fit to page when opened
  %pdfnewwindow=true, % links in new window
  %colorlinks=true,           % false: boxed links; true: colored links
  %linkcolor=blue,            % color of internal links
  %citecolor=magenta,    % color of links to bibliography
  %filecolor=magenta,     % color of file links
  %urlcolor=cyan              % color of external links
%}
\usepackage{graphicx}
\graphicspath{ {figures/} }

\newcommand{\thornado}{\texttt{thornado}}
\newcommand{\ee}[1]{{\color{blue} #1}}

@@

We apply the method of lines approach to temporal discretization.  
With the spatial discretization specified, the DG problem in Eq.~\eqref{eq:semidiscreteDG} can be viewed as a system of ordinary differential equations (ODEs) for the expansion coefficients $\boldsymbol{C}=\{\boldsymbol{C}_{j}\}_{j=0}^{k}$, i.e.,
\begin{equation}
  d_{t}\boldsymbol{C}
  =\boldsymbol{L}(\boldsymbol{C}),
\end{equation}
which can be discretized in time.  
To this end, we apply the strong stability-preserving Runge-Kutta (SSP-RK) methods of order 1 to 3 \citep{gottlieb_etal_2001}.  
The 1st order method (SSP-RK1) is simply the forward Euler method, while the 2nd and 3rd order methods (SSP-RK2 and SSP-RK3, respectively) can be expressed as convex combinations of forward Euler steps.  
A general $m$-stage Runge-Kutta method is given by
\begin{align}
  \boldsymbol{C}^{(0)}
  &=\boldsymbol{C}^{n} \\
  \boldsymbol{C}^{(i)}
  &=\sum_{l=1}^{i-1}\alpha_{il}\,\big(\,\boldsymbol{C}^{(l)}+\beta_{il}\,\Delta t\,\boldsymbol{L}(\boldsymbol{C}^{(l)})\,\big)
  \quad i=1,\ldots,m \\
  \boldsymbol{C}^{n+1}
  &=\boldsymbol{C}^{(m)},
\end{align}
where $\alpha_{il},\beta_{il}\ge0$ are given by Butcher tables.  
During time integration, we apply slope and positivity limiters after each stage as a post-processing step.

In the numerical experiments presented below, we will vary the spatial and temporal order of the method.  
The 1st order method (DG(0)+RK1) uses polynomials of degree $0$ in each element and the forward Euler time integration method, the second-order method (DG(1)+RK2) uses polynomials of degree $1$ combined SSP-RK2 time integration, while the 3rd order method (DG(2)+RK3) uses polynomials of degree $2$ combined SSP-RK3 time integration.

@@

Several tests were used to assess the accuracy of the integration method \citep{LiskaWendroff2003}. 
\begin{table}[h!]
\begin{center}
\begin{tabular}{ |c|c c c|c c c|c c| }
 \hline
 Test & $\rho_L$ & $u_L$ & $p_L$ & $\rho_R$ & $u_R$ & $p_R$ & $x_0$ & T \\
 \hline
 1 & 1 & 0 & 1 & 0.125 & 0 & 0.1 & 0.5 & 0.2 \\
 2 & 1 & 0.75 & 1 & 0.125 & 0 & 0.1 & 0.3 & 0.2 \\
 3 & 1 & -2 & 0.4 & 1 & 2 & 0.4 & 0.5 & 0.15 \\
 4 & 1 & 1 & $10^{-6}$ & 1 & -1 & $10^{-6}$ & 0.5 & 1 \\
 5 & 1 & -19.59745 & 1000 & 1 & -19.59745 & 0.01 & 0.8 & 0.012 \\
 6 & 5.99924 & 19.5975 & 460.894 & 5.99242 & -6.19633 & 46.095 & 0.4 & 0.035 \\
 7 & 1.4 & 0 & 1 & 1 & 0 & 1 & 0.5 & 2 \\
 8 & 1.4 & 0.1 & 1 & 1 & 0.1 & 1 & 0.5 & 2 \\
 9 & 0.1261192 & 8.9047029 & 782.92899 & 6.591493 & 2.2654207 & 3.1544874 & 0.5 & 0.0039 \\
10 & 5.6698 & 9.0299 & 100 & 1.0 & 0.0 & 1.0 & 0 & 1 \\
11 & 5.6698 & −1.4701 & 100 & 1.0 & -10.5 & 1.0 & 0 & 1 \\
 \hline
\end{tabular}
  \caption{table of tests \ee{Add more descriptive caption}}
  \label{tab:testtable}
\end{center}
\end{table}
$x_0$ refers to the position of the barrier. 
The computational domain $D$ is defined with $x_{\mbox{\tiny L}}=0.0$ and $x_{\mbox{\tiny R}}=1.0$ in tests 1--8, 0.1 to 0.6 in test 9 \citep{LiskaWendroff2003}, -5 to 15 in test 10, and -15 to 5 in test 11 \citep{Leveque2002}. 
\ee{Provide more detailed description of the Riemann problems and refer to Table~\ref{tab:testtable}}
